\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-04-27 paper_final.tex
Wrote algorithm for bounding etat

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{bbm}
\usepackage{parskip}

@@

@@

\section{Teaching Dimension}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{bbm}
\usepackage{parskip}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{color}

@@

\newcommand{\learn}{\mathcal{A}_{w_0}^\eta}

@@

\section{Teaching Dimension}
\cite{perceptron} used two metrics when analyzing their teaching strategies. The first was the exact 
teaching dimension. The exact teaching dimension is the length of the shortest training sequence that 
teaches a learner the desired concept.

\subsection{$TD_{exact}$}

Formally, let $\mathbb{S}$ be the space of finite training 
sequences. Then let $\mathcal{A}_{w_0}^{\eta} : \mathbb{S} \to \mathbb{R}^d$ be a function the gives the 
resultant weight vector after training on a sequence in $\mathbb{S}$, where $w_0$ is the initial weight 
vector, and $\eta$ is the learning rate. Then if the teacher which to teach a concept $w^*$, then since $w^*$ describes a linear decision boundary then for any $c > 0$, $cw^*$ is parameterizes the same concept as $w^*$
so the exact teaching dimension is 
$$
TD_{exact}(w^*, \mathcal{A}_{w_0}^\eta) = \min\{ \lvert S \rvert : 
\mathcal{A}_{w_0}^\eta(S) = cw^* \text{ for some } c >0 \}
$$

\cite{perceptron} showed that when $\eta$ and $w_0$ where known, $TD_{exact}(w^*, \mathcal{A}_{w_0}^\eta) = 1$

\subsection{$TD_\epsilon$}
\cite{perceptron} also defined an approximate teaching dimension for cases where the exact teaching dimension was infinite but one could approximately teach a concept within $\epsilon$ distance. For perceptrons, the distance metric used was simply the 1 minus the cosine angle between $w^*$ 
and $\learn(S)$
$$
1 -\frac{\langle \learn(S), w^* \rangle}{\lVert \learn(s) \rVert \lVert w^* \rVert} \leq \epsilon
$$

Then let $\mathbb{T}_\epsilon$ be the set of $\epsilon-\text{approximate}$ teaching strategies for a decision boundary $w^*$. Then
$$
TD_\epsilon(w^*, \learn) = \min_{t \in 
\mathbb{T}_\epsilon} \max_{w_0 \in 
\mathbb{R}^d} \lvert t(w_0) \rvert
$$

\cite{perceptron} showed that when $w_0$ was unknown but $\eta$ was known $TD_\epsilon(w^*, \learn) = 3$

\section{Approximate Teaching with Unkown $\eta$}
Now we look at the scenario where the initial weight vector is known but the learning rate is unknown and bounded.

\subsection{Using Unlabeled Examples}
Before the teaching dimension was only analyzed with labeled examples. Here we relax this constraint and allow unlabeled examples to be used in the teaching sequence. Now we redefine $\mathbb{S}$ to be the set of all sequences of labeled and unlabeled examples. And for any $S \in \mathbb{S}$
$$
\learn(S) = \learn(S \setminus \{s \in S : s = (x, ?)\} )
$$

\subsection{Algorithm for bounding $\eta$}
With the ability to teach with unlabeled examples, below shows the optimal algorithm for bounding $\eta$ within a desired length, under the conditions that $\eta$ is bounded and $w_0$ is known a priori.

\begin{algorithm}
\caption{Bounding $\eta$ within $\epsilon$ }
\begin{algorithmic}[1]
	\REQUIRE $\epsilon$ , lower bound $\eta_{\min} > 0$, upper bound $\eta_{\max} < \infty$ and $w^*$
	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = 1 = 
	-sign(\langle w_0 , x_1 \rangle )$
	\STATE Give $(x_1, y_1)$ to the perceptron and allow to update.
	\STATE $\alpha \leftarrow \eta_{\min}$
	\STATE $\beta \leftarrow \eta_{\max}$

	\WHILE{$\beta - \alpha > \epsilon$}
		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
		\IF{$\hat{y} = 1$}
			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 		
		\ELSE
			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 
		\ENDIF	
	\ENDWHILE   
	\RETURN $(\alpha , \beta)$
\end{algorithmic}
\end{algorithm}

\section*{Theorem 1}
If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$ examples.=

\subsection*{Proof:}
Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = 1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
\color{red}
I don't think that its hard to show this is true.
\color{black}

Then give $(x_1, y_1)$ to the learner and then after training update,
$$
w_1 = w_0 + \eta* x_1
$$

Then grab an unlabeled $x_2$ such that
$\langle w_0,x_2 \rangle \neq 0$, $\langle x_1, x_2 \rangle \neq 0$
and 
$$
\langle w_0,x_2 \rangle + \frac{\beta - \alpha}{2} \langle x_1, x_2 \rangle = 0
$$
\color{red}
I'm a moron. What's the closed form of this? I know there is not a unique solution. We just need the simplest one.
\color{black}

Then probe the learner with $x_2$. If the learner outputs $+1$ then
$\eta \in (\frac{\beta - \alpha}{2} , \beta]$, else 
$\eta \in [\alpha,\frac{\beta - \alpha}{2}]$
